---
title: "Assignment 1"
output:
  pdf_document: default
  html_document: default
---

## Question 1
```{r}
# question 1
apply(Titanic, c(1, 4), sum)
apply(Titanic, c(2, 4), sum)
apply(Titanic, c(3, 4), sum)

```


## Question 2

```{r}
# question 2
set.seed(1234)
k <- rnorm(1000)
sum(k < -1.65 | k > 1.65)/1000
```

10 % of the generate numbers are outside the -1.645, 1.645 limit. This matches our expectation because 1.65 is 1.65 standard deviations from the mean and we know that 10% of values should be outside the 1.65 standard deviation range. 
## Question 3

```{r}
# question 3
breaks <- c(-99999,-1.645,1.645,99999)
x <- rnorm(1000)
t <- table(cut(x,breaks))
names(t) <- c('small', 'medium', 'large')
t
```

## Question 4

```{r}
# question 4
rnd <- round(runif(1000,0,1000))
sum(rnd %% 5 == 0)

```
 This matches out expectation. Randomly generated numbers should have 20% divisible by 5 because 20% of all numbers are divisible by 5.

## Question 5

```{r}
# question 5
f_day <- function(year) {
  return (paste(toString(year),'-01-01',sep=''))
}

l_day <- function(year) {
  return (paste(toString(year),'-12-31',sep=''))
} 

all_days <- function(year){
  return(table(weekdays(seq(as.Date(f_day(year)), as.Date(l_day(year)), by="days"))))
  
}

for (year in c(2011:2020)) {
  print(year)
  print(all_days(year))
}

```

## Question 6 

```{r}
dat <- read.delim('Groceries_dataset.csv', header=TRUE)

# number of rows and columns
dim(dat)

#summary of data
summary(dat)

```
