---
title: "presentation"
author: "William Li"
date: "26/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# import libraries
library(MASS)
library(corrplot)
library(ggplot2)
library(dplyr)
library(ggpubr)

```

## Simple Preprofiling

```{r}
data <- Boston
summary(Boston)
head(Boston)
dim(Boston)
sapply(Boston,class)
```

## Description of Features

```{r}
# dictionary like object to make retrieving the description of each variable easy
lw <- list(crim = 'Crime Rate',
           zn = 'Proportion over 25 000sqft',
           indus = 'Proportion of Non-Businesses',
           chas = 'Besides Charles River',
           nox ='Nitrogen Oxide Concentration',
           rm = 'Average Number of Rooms',
           age = 'Proportion Built Before 1940',
           dis = 'Dist. From Employment Centres',
           rad = 'Accessibility to Highways',
           tax = 'Property Tax Rate / $ 10 000',
           lstat = 'Percent Lower Status',
           medv = 'Median Value of Homes')

lw['indus']

```




## Histogram of All Features

```{r, echo=TRUE}
par(mfrow = c(3,5), mai = c(0.3, 0.6, 0.5, 0.1))
mapply(function(x,y) hist(x,main=y),
       Boston,
       colnames(Boston)) %>% invisible()
```

# Normality of "rm"
```{r}
par(mfrow = c(1,2))
hist(data$rm, freq=FALSE, ylim = c(0,0.8))
lines(density(data$rm), lwd=2, col='Blue')
qqnorm(data$rm)

```



## Feature Engineering 

The "crim" variable is very skewed to the left. It is difficult to visualize results with it
```{r}

par(mfrow=c(1,2), mar=c(4,5,2,2))
hist(Boston$crim,breaks=40, 
     main='Histogram of Crime Rate',
     xlab='Crime Rate')
plot(Boston$crim,
     Boston$medv, 
     main = 'Home Value vs Crime Rate', 
     xlab='Crime Rate',
     ylab = 'Median Home Value')

```

Applying a log transformation produces better results
```{r}

par(mfrow=c(1,2), mar=c(4,4,2,3))
# apply log transformation
data$crim <- log(Boston$crim)
hist(data$crim, main='Histogram of log(Crime Rate)', 
     xlab='log(Crime Rate)')
plot(data$crim,data$medv, 
     main='Median Home Value vs \nlog(Crime Rate) \n', 
     xlab='log(Crime Rate)', ylab='Median Home Value')
abline(lm(data$medv~data$crim), col='Blue')

```

Drop "black" feature, unsure how to use parabolic transformation and uninvertible function
```{r}
data$black <- NULL

```

## Correlation Plot

A correlation plot is great for looking for relationships between features 

```{r}

corrplot(cor(data), 
         method='color', 
         type='lower', 
         diag=FALSE, 
         cl.pos="r", 
         title = , 
         addCoef.col = "black",
         tl.srt = 90, 
         number.cex = .6)
mtext("Correlation Plot of Boston Dataset", 
      at=6, 
      line=2, 
      cex=1)

```

```{r}
two.plot <- function(x,y){
  g <- ggplot(data=data, aes_string(x=x,y=y)) +
    geom_point() + 
    geom_smooth(method = 'lm') +
    ggtitle(paste(lw[y],' \nvs ', lw[x])) + 
    ylab(lw[y]) + 
    xlab(lw[x]) 
}

# put onto same plot
ggarrange(two.plot('rm','medv'),
          two.plot('age','dis'),
          ncol = 2, nrow = 1)
```

A ANOVA model was built with all the possible interactions to look for interesting interactions
```{r}
summary(aov(data=data, medv ~ .^2 )) %>% invisible()
```

## Interaction Plots

```{r}
bins <- c('low','medium','high')
data.c <- data.frame(apply(data,2,function (x) cut(x,3,bins))) 

attach(data.c)

# ordered the levels to makes sure it appears in the right order in plots.
ord <- function(x){
  return(factor(x,level=c('low','medium','high')))
}

par(mfrow = c(2,2), mar = c(4,4,3,3))
interaction.plot(ord(indus), 
                 lstat,
                 Boston$medv,
                 xlab='indus',
                 trace.label = lw['lstat'])

interaction.plot(ord(crim),
                 rm,
                 Boston$medv,
                 xlab='crim')

interaction.plot(ord(crim),
                 lstat,
                 Boston$medv,
                 xlab='crim')

interaction.plot(ord(nox),
                 Boston$chas,
                 Boston$medv,
                 xlab='rad')

mtext("Interesting Interactions", at=0, line=18, cex=1)


```
## 3 Variable Plots
```{r}
bins <- c('low','medium','high')
data.c <- data.frame(apply(data,2,function (x) cut(x,3,bins))) 
colnames(data.c) <- paste(colnames(data.c),'.c', sep='')
data.all <- cbind(data,data.c)

ggplot(data=data.all) + 
  geom_histogram(aes(x=crim, color=age.c, fill=age.c, y=0.333*..density..), 
                 alpha=0.3, position='identity',bins=20) +
  scale_color_manual(values = rainbow(3)) +
  scale_fill_manual(values = rainbow(3)) + 
  geom_density(aes(x=crim,color=age.c, y=0.333*..density..)) + 
  ggtitle(paste('Distribution of Crime Rates by Suburb',lw['age'])) +
  labs(fill="Proportion Before 1940") +
  guides(color=FALSE) +
  ylab('Density') + xlab(lw['crim'])



```

```{r}

ggplot(data=data.all,
       aes(x=crim,y=medv, color=lstat.c)) + 
  geom_point() + 
  ggtitle(paste(lw['medv'],'vs',lw['crim'],'by',lw['lstat'])) + 
  stat_smooth(method=lm) +
  labs(color=lw['lstat']) +
  ylab(lw['medv']) + xlab(lw['crim'])

```

```{r}

ggplot(data=data.all,
       aes(x=rm,y=medv, color=crim.c)) + 
  geom_point() + 
  stat_smooth(method=lm) +
  ggtitle(paste(lw['medv'],
                'vs',lw['rm'],
                'by',lw['crim'])) +
  ylab(lw['medv']) +
  xlab(lw['rm']) +
  labs(color=lw['crim'])
  
```



