---
title: "presentation"
author: "William Li"
date: "26/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# import libraries
library(MASS)
library(corrplot)
library(ggplot2)
library(dplyr)
library(ggpubr)

data <- Boston

```

## Simple Preprofiling

```{r}
summary(Boston)
head(Boston)
dim(Boston)
sapply(Boston,class)
```

## Description of Features

```{r}
# dictionary like object to make retrieving the description of each variable easy
lw <- list(crim = 'Crime Rate',
           zn = 'Proportion over 25 000sqft',
           indus = 'Proportion of Non-Businesses',
           chas = 'Besides Charles River',
           nox ='Nitrogen Oxide Concentration',
           rm = 'Average Number of Rooms',
           age = 'Proportion Built Before 1940',
           dis = 'Distance From Employment Centres',
           rad = 'Accessibility to Highways',
           tax = 'Property Tax Rate / $ 10 000',
           lstat = 'Percent Lower Status',
           medv = 'Median value of Homes')

lw['indus']

```




## Histogram of All Features

```{r, echo=TRUE}
par(mfrow = c(3,5), mai = c(0.3, 0.6, 0.5, 0.1))

mapply(function(x,y) hist(x,main=y),
       Boston,
       colnames(Boston)) %>% invisible()
```

# Normality of "rm"
```{r}
par(mfrow = c(1,2))
hist(data$rm, freq=FALSE, ylim = c(0,0.8))
lines(density(data$rm), lwd=2, col='Blue')
qqnorm(data$rm)

```



## Feature Engineering 

The "crim" variable is very skewed to the left. It is difficult to visualize results with it
```{r}
par(mfrow=c(1,2), mar=c(4,5,2,2))
hist(Boston$crim,breaks=40)
plot(Boston$crim,Boston$medv, main = 'Home Value vs Crime Rate')

```

Applying a log transformation produces better results
```{r}
par(mfrow=c(1,2), mar=c(4,4,2,3))
# apply log transformation
data$crim <- log(Boston$crim)
hist(data$crim)
plot(data$crim,data$medv, main='medv vs crim')
abline(lm(data$medv~data$crim), col='Blue')
```

Drop "black" feature, unsure how to use parabolic transformation and uninvertible function
```{r}
data$black <- NULL

```

## Correlation Plot

A correlation plot is great for looking for relationships between features 

```{r}
corrplot(cor(data), method='color', type='lower', diag=FALSE, cl.pos="r", 
         title = , addCoef.col = "black",
         tl.srt = 90, number.cex = .6)
mtext("Correlation Plot of Boston Dataset", at=6, line=2, cex=1)

```

```{r}
two.plot <- function(x,y){
  wrapper <- function(x, ...) 
  {
    paste(strwrap(x, ...), collapse = "\n")
  }
  
  g <- ggplot(data=data, aes_string(x=x,y=y))
  g + geom_point() + geom_smooth(method = 'lm') +
    ggtitle(wrapper(paste(lw[y],' vs ', lw[x]))) + ylab(lw[y]) + 
    xlab(lw[x])
}
# put onto same plot
ggarrange(two.plot('rm','medv'),
          two.plot('age','dis'),
          ncol = 2, nrow = 1)


```

A ANOVA model was built with all the possible interactions to look for interesting interactions
```{r}
summary(aov(data=data, medv ~ .^2 ))
```

## Interaction Plots

```{r}
bins <- c('low','medium','high')
data.c <- data.frame(apply(data,2,function (x) cut(x,3,bins))) 

attach(data.c)

# ordered the levels to makes sure it appears in the right order in plots.
ord <- function(x){
  return(factor(x,level=c('low','medium','high')))
}

par(mfrow = c(2,2), mar = c(4,4,3,3))
interaction.plot(ord(indus), 
                 lstat,
                 Boston$medv,
                 xlab='indus')

interaction.plot(ord(crim),
                 rm,
                 Boston$medv,
                 xlab='crim')

interaction.plot(ord(crim),
                 lstat,
                 Boston$medv,
                 xlab='crim')

interaction.plot(ord(nox),
                 Boston$chas,
                 Boston$medv,
                 xlab='rad')

mtext("Interesting Interactions", at=0, line=18, cex=1)


```

